scoring

### 2022-04-16 darts/scoring.Rmd
Spent a little too much time on this :grimacing:

>>>>

Trying to get single curves set up here
```{r}
plot_single <- function(data, case_, iter_) {
    # I checked that both "Truth" cases are the same between models but potential error source here -- should rethink csv saving
    t_data <- data %>% 
                filter(case == case_ & iter == iter_) %>% 
                transform(ml_model = ifelse(true_model==TRUE, "Truth", ml_model)) %>% 
                transform(true_model = ifelse(ml_model == "Truth", FALSE, true_model))

    t_data %>% 
        filter(case == case_ & iter == iter_ & true_model == FALSE) %>%
        group_by(time, true_model, ml_model) %>% 
        mutate(`5%` = quantile(value, c(.05))) %>% 
        mutate(`95%` = quantile(value, c(.95))) %>% 
        ggplot() +
        geom_ribbon(aes(x=time, ymin=`5%`, ymax=`95%`, color=ml_model, fill=ml_model), alpha=0.4)
}

plot_single(data, "nontipped", 0)

```

```{r}
plot_single(data, "tipped", 1)
```
